Reducing iptables configuration complexity using chains

### 2014-05-04 iptables/paper.tex
add section about rule order

>>>>

    \subsection{Putting it all together}
    All rules are checked one for one, and if one matches the target is executed, in this case, the packet is accepted :
    \begin{verbatim}
iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT
iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT
iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT
iptables -A INPUT -j DROP
    \end{verbatim}
    The last rule matches everything, so if a packet didn't match a previous rule, it will be rejected.\\
    \textbf{Remark:} the order of the rules is important.
